\section{LAB}
\begin{frame}{}
    \centering
        \Huge\bfseries
    \textcolor{yellow}{LAB}
\end{frame}

\begin{frame}{Promise.Any.Call leaks "TheHole" Value -- CVE-2022-4174}{Discovered by Zhenghang "kiprey" Xiao -- Independent Security Researcher}
    \begin{columns}
        \begin{column}{0.55\textwidth}
            \begin{itemize}
                \item This bug functionally behaves identical to Json.stringify's hole leak.
                \item There are plenty of exploits for TheHole online. 
                \item Download a specific version from \href{https://commondatastorage.googleapis.com/v8-asan/index.html}{\color{pink}here}.
                    \begin{itemize}
                        \item Version '77090' will work for this exploit.
                        \item Use 'linux-release' to pop a calculator.
                        \item Use 'linux-debug' when not trying to exploit.
                        \item Use '--gdbjit-full' in your command line! 
                    \end{itemize}
            \end{itemize}
        \href{https://bugs.chromium.org/p/chromium/issues/detail?id=1379054}{\color{pink}{crbug-1379054}} \\
        Try it yourself! Try and understand every line of code by leaving a comment. 
        \end{column}
        \begin{column}{0.4\textwidth}
            \usemintedstyle{vim}
            \inputminted{js}{code/promise.tex}
        \end{column}
    \end{columns}
    \note{
        \begin{itemize}
            \item Promise.Any.Call was patched in Chrome 106.
            \item This vulnerability is exploitable from Chrome 86-106.
            \item Zhenghang Xiao is still an active Chrome VRP researcher, ranking 3rd in bug bounties in Chrome.
            \item He has a black hat talk, it's pretty cool. 
        \end{itemize}
    }
\end{frame}
